Staged Abstract Interpreters

### 2018-10-29 paper/50_cases.tex
add ref

Beyond control-flow analysis, staging data structures used in the abstract interpreter, such as abstract domain.
It has been shown that specializing abstract domains with respect to the structure of analyzed program significantly 
improves the performance: a recent example is online decomposition of polyhedra \cite{DBLP:conf/popl/SinghPV17}.
In this section, we present a similar idea for interval abstract domain using an \textit{offline} fashion by staging.

>>>>

Beyond control-flow analysis, staging data structures used in the abstract interpreter, such as abstract domain.
It has been shown that specializing abstract domains with respect to the structure of analyzed program significantly 
improves the performance: a recent example is online decomposition of polyhedra \cite{DBLP:conf/popl/SinghPV17, Singh:2017:PCD:3177123.3158143}.
In this section, we present a similar idea for interval abstract domain using an \textit{offline} fashion by staging.
